\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{xcolor}
\usepackage[urlbordercolor=black,pdfborderstyle={/S/U/W 1}]{hyperref}

\title{
    Julian Fortune's Resumé
}
\author{
    Julian Fortune
}

%% These are custom commands defined in scimisc-cv.sty
\cvname{
    Julian Fortune
}
\cvpersonalinfo{
            whatever \cvinfosep
                me@gmail.com \cvinfosep
                \href{http://linkedin.com/in/julianfortune/}{LinkedIn} \cvinfosep
                \href{http://linkedin.com/in/julianfortune/}{GitHub} \cvinfosep
    }

%
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\large

\makecvtitle

\hypertarget{education}{%
\section{Education}\label{education}}

\experience{%
    Oregon State University
}{%
    Honors Bachelor of Science
}{%
    Graduated June 2021 
}

\begin{itemize}
\tightlist
\item
  Computer Science major focusing on Artificial Intelligence with a 4.0
  GPA.
\item
  Relevant courses: Parallel Programming, Android Development, \& Deep
  Learning
\item
  Clubs: App Dev Club president \& graphic designer, and Artificial
  Intelligence Club member.
\end{itemize}

\hypertarget{experience}{%
\section{EXPERIENCE}\label{experience}}

\experience{%
    Skyworks Solutions
}{%
    Machine Learning Co-op
}{% 
    January 2021 -- Present
}

\begin{itemize}
\tightlist
\item
  Assisting with experiments, overseeing cloud resources (e.g.,
  MongoDB), \& writing tests in Python.
\end{itemize}

\experience{%
    Lucid Software
}{%
    Software Engineering Intern
}{%
    June 2020 -- September 2020
}

\begin{itemize}
\tightlist
\item
  Aided in developing an algorithm to classify hand-drawn shapes and
  identify squiggles.
\item
  Redesigned the paywall system using Angular and Typescript to support
  a suite of products.
\end{itemize}

\experience{%
    Oregon Health \& Science University
}{%
    Volunteer Software Engineer
}{%
    November 2019 – Present
}

\begin{itemize}
\tightlist
\item
  Creating a computer vision system and desktop application using
  Python, OpenCV, and PyQt.
\end{itemize}

\experience{%
    Oregon State University
}{%
    Teaching Assistant
}{%
    September 2019 -- December 2020 
}

\begin{itemize}
\tightlist
\item
  Leading labs of 30+ students, grading, and assisting students with
  Computer Science courses.
\end{itemize}

Human-Machine Teaming Laboratory, CoRIS --- Research Assistant February
2018 -- Present

\begin{itemize}
\tightlist
\item
  Designed, developed, and validated an algorithm that estimates
  workload in real-time based on audio features and a neural network
  built using TensorFlow \& TFLearn libraries, written in Python.
\end{itemize}

CBTNuggets --- Software Engineering Intern June 2018 -- June 2019

\begin{itemize}
\tightlist
\item
  Debugged, fixed crashes, implemented features, and wrote tests for the
  iOS, tvOS, and UWP apps.
\item
  Added practice exams to iOS app, speed controls to tvOS app, and
  leaderboards to the UWP app.
\end{itemize}

\hypertarget{select-publications}{%
\section{SELECT PUBLICATIONS}\label{select-publications}}

\begin{itemize}
\tightlist
\item
  J. Fortune, J. Heard, and J. Adams, ``Real-Time Speech Workload
  Estimation for Intelligent Human- Machine Systems,'' 2020. Human
  Factors and Ergonomics Society Annual Meeting, 2020.
\item
  J. Fortune, ``Real-time Speech Workload Estimation.'' (Undergraduate
  Honors Thesis). May 2020.
\end{itemize}

\hypertarget{projects}{%
\section{PROJECTS}\label{projects}}

\begin{itemize}
\tightlist
\item
  \textbf{Functional-C}: Statically-typed, interpreted, side-effect-free
  language written in Haskell.
\item
  \textbf{Tweet Sentiment Extraction (Kaggle)}: Classifies the sentiment
  of tweets using a highly-modified version of a Naïve Bayes classifier
  and intelligent pre-processing. Achieved a .66 accuracy score.
\item
  \textbf{Jumble}: A JS app for unscrambling `jumbled' words and listing
  all matches instantaneously.
\end{itemize}

\hypertarget{awards}{%
\section{AWARDS}\label{awards}}

\begin{itemize}
\tightlist
\item
  1st Place Team in Lucid Hackathon --- Lucid Software August 2020
\item
  College of Engineering Dean's List --- Oregon State University
  September 2018 -- Present
\end{itemize}

\hypertarget{skills}{%
\section{SKILLS}\label{skills}}

\begin{itemize}
\tightlist
\item
  LANGUAGES: Swift, Python, Kotlin, Scala, C++, C, C\#, Typescript,
  Haskell, JS, SQL, \& Golang. - TECH: Linux, MongoDB, Git, Angular,
  PyTorch, TensorFlow, OpenCV, \& CUDA.
\end{itemize}

\end{document}