% Adapted from: "Scismic's Recommended CV Template for Biotech and Pharma Jobs" by Scismic and Overleaf, licensed under [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/), accessed April 10, 2020 from [Overleaf](https://www.overleaf.com/latex/templates/scismics-recommended-cv-template-for-biotech-and-pharma-jobs/hbnkjrjnnpjz)

\documentclass[10pt]{article} % decrease fontsize to `10pt` or `11pt` to make more room


%% Dependencies %%

\usepackage{enumitem}
\usepackage{geometry}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{paracol}
\usepackage{parskip}
\usepackage{soul}  % \ul
\usepackage{textcase}
\usepackage[compact,small,explicit]{titlesec}  % Used for `titleformat`
\usepackage[x11names]{xcolor}

% Depended upon by `pandoc`'s markdown conversion
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}


%% Fonts %%

\usepackage[defaultsans]{cantarell}
% Changes the default font family to sans-serif (instead of serif)
\renewcommand*\familydefault{\sfdefault}
% Force using an 8-bit encoding (instead of 7)
\usepackage[T1]{fontenc}


%% Formatting Configuration %%

\setlist{leftmargin=*,nosep}

% Make `\ul` from `soul` look like standard underline
\setul{1pt}{.4pt}

% Turn off ugly blue boxes for links
\hypersetup{colorlinks=true, urlcolor=black}


%% Format Headers %%

% Set custom formatting for H1
\titleformat{\section}%
  {\Large}% Font size
  {\thesection}{0pt}%
  {{%
    \fontfamily{Nunito-TLF}\selectfont% Use rounded font
    \textls[15]{% Increase character spacing
      \MakeTextUppercase{#1}%
    }}%
  }%
  [{\color{gray}\titlerule[0.5pt]}] % Horizontal rule beneath text

% Increase H1 margin-top
\titlespacing{\section}{0pt}{10pt}{5pt}  % left / above / below

% Use rounded font for H2
\titleformat{\subsection}%
  {\large\bfseries\fontfamily{Nunito-TLF}\selectfont}% Font style
  {\thesection}{0pt}%
  {#1}

% Increase H2 margin-top
\titlespacing{\subsection}{0pt}{7pt}{5pt}  % left / above / below

% Make H3's gray & use rounded font
\titleformat{\subsubsection}
   {\small\bfseries\fontfamily{Nunito-TLF}\selectfont}%
   {\thesection}{0pt}%
   {\textcolor{gray}{#1}}


%% Commands %%

% Store a reference to the original `href` command
% Source: https://tex.stackexchange.com/a/47353
\let\defaultref\href

% Override `href` to add an underline via `\ul`, which fixes underlines without
% needing to use `\smash`--which breaks padding
\renewcommand{\href}[2]{%
  \defaultref{#1}{\ul{#2}}%
}

\newcommand{\link}[2]{\href{#1}{#2}}

% Override `href` to add an underline via `\ul`, which fixes underlines without
% needing to use `\smash`--which breaks padding
\renewcommand{\emph}[1]{%
  \textcolor{gray}{#1}%
}

% Byline with contact info / links
\def\separator{ · {}}

\newcommand{\name}[1]{%
  \begin{center}
      {\huge\bfseries\MakeTextUppercase{#1}\par}
  \end{center}
}

%% Document Configuration %%

\geometry{a4paper,margin=0.5in}
\pagestyle{empty}
\setcounter{secnumdepth}{0}


%% Document metadata %%
% NOTE: Variables come from markdown front-matter via `pandoc` conversion.

\title{Julian Fortune's Resumé}
\author{Julian Fortune}


%% Document definition %%

\begin{document}

% Name (title)
\begin{bfseries}\begin{huge}
  {\fontfamily{Nunito-TLF}\selectfont%
    \MakeTextUppercase{Julian Fortune}
  }
\end{huge}\end{bfseries}

% Contact info
  \link{https://forms.gle/KkSirNbEgQozTH2x7}{Contact}\separator%
% Public info
    \link{http://github.com/julianfortune}{GitHub}\separator%
\link{http://linkedin.com/in/julianfortune}{LinkedIn}%

% \begin{raggedright}

\columnratio{0.75}
\begin{paracol}{2}
\setlength{\columnsep}{1em}

\hypertarget{experience}{%
\section{Experience}\label{experience}}

\hypertarget{mccourt-global-technology-aug-2023-present}{%
\subsection{\texorpdfstring{McCourt Global Technology \hfill \small Aug
2023 --
Present}{McCourt Global Technology Aug 2023 -- Present}}\label{mccourt-global-technology-aug-2023-present}}

\vspace{-3pt}

\hypertarget{sr.-software-engineer-project-liberty-labs-jan-2025-present}{%
\subsubsection{\texorpdfstring{\small Sr.~Software Engineer (Project
Liberty Labs) \hfill \small Jan 2025 --
Present}{Sr.~Software Engineer (Project Liberty Labs) Jan 2025 -- Present}}\label{sr.-software-engineer-project-liberty-labs-jan-2025-present}}

\vspace{-3pt}

\hypertarget{software-engineer-project-liberty-labs-jan-2024-jan-2025}{%
\subsubsection{\texorpdfstring{\small Software Engineer (Project Liberty
Labs) \hfill \small Jan 2024 -- Jan
2025}{Software Engineer (Project Liberty Labs) Jan 2024 -- Jan 2025}}\label{software-engineer-project-liberty-labs-jan-2024-jan-2025}}

Transferred to a back-end team at a different startup building the user
authentication and SSO for a social media platform (Frequency) based on
an open source protocol.

\begin{itemize}
\tightlist
\item
  Promoted within a year for outstanding performance and taking
  ownership of projects.
\item
  Created an end-to-end test suite for a Spring application using
  Playwright.
\item
  Developed support for passwords and passkeys as authentication
  methods.
\item
  Built out a separate service for sending SMS messages with
  fraud-prevention logic.
\item
  \textbf{Stack}: Kotlin, Spring, Redis, and Postgres
\end{itemize}

\hypertarget{software-engineer-elemint-aug-2023-jan-2024}{%
\subsubsection{\texorpdfstring{\small Software Engineer (Elemint)
\hfill \small Aug 2023 -- Jan
2024}{Software Engineer (Elemint) Aug 2023 -- Jan 2024}}\label{software-engineer-elemint-aug-2023-jan-2024}}

Hired to work across the stack and bring functional programming
experience to a startup building a customer loyalty product for a French
soccer league.

\begin{itemize}
\tightlist
\item
  Developed React components using Tailwind CSS, implemented endpoints,
  added front-end features, and wrote Postgres migrations.
\item
  Mentored peers and championed usage of algebraic data types and
  generic typing.
\item
  Transformed requirements into concrete technical specifications and
  tickets
\item
  \textbf{Stack}: Typescript, React, Storybook, NextJS, and tRPC.
\end{itemize}

\hypertarget{disney-streaming-software-engineer-june-2022-aug-2023}{%
\subsection{\texorpdfstring{Disney Streaming \emph{· \small Software
Engineer} \hfill \small June 2022 -- Aug
2023}{Disney Streaming · Software Engineer June 2022 -- Aug 2023}}\label{disney-streaming-software-engineer-june-2022-aug-2023}}

Recruited to a Scala team focusing on tools for AWS Kinesis, including
schema registry, code generation, and producer and consumer SDKs.

\begin{itemize}
\tightlist
\item
  Added features to SDK's, `higher-level' services (e.g., snapshotter),
  and SBT plugins.
\item
  Analyzed and optimized AWS usage, resulting in annual savings over
  \$1M.
\item
  Added Python support to the code generation plugin, which outputs a
  custom library with classes corresponding each event defined in a
  given schema registry.
\item
  \textbf{Stack}: Typelevel Scala, AWS Kinesis,Terraform, and Smithy.
\end{itemize}

\hypertarget{agot-ai-june-2021-june-2022}{%
\subsection{\texorpdfstring{Agot AI \hfill \small June 2021 -- June
2022}{Agot AI June 2021 -- June 2022}}\label{agot-ai-june-2021-june-2022}}

\vspace{-5pt}

\hypertarget{training-data-team-lead}{%
\subsubsection{\texorpdfstring{\small Training Data Team
Lead}{Training Data Team Lead}}\label{training-data-team-lead}}

Promoted to lead the team responsible for processing videos and creating
training labels.

\begin{itemize}
\tightlist
\item
  Planned sprints, conducted interviews, and tracked the team's
  progress.
\item
  Doubled the rate of training data produced through process
  improvements.
\end{itemize}

\hypertarget{software-engineer}{%
\subsubsection{\texorpdfstring{\small Software
Engineer}{Software Engineer}}\label{software-engineer}}

Hired to develop integrations and algorithms for a computer vision
feedback system.

\begin{itemize}
\tightlist
\item
  Implemented microservices in Python communicating via RabbitMQ.
\item
  Wrote Python libraries for standardizing consuming and producing
  RabbitMQ events
\end{itemize}

\hypertarget{skyworks-solutions-software-engineer-intern-jan-2021-june-2021}{%
\subsection{\texorpdfstring{Skyworks Solutions \emph{· \small Software
Engineer (Intern)} \hfill \small Jan 2021 -- June
2021}{Skyworks Solutions · Software Engineer (Intern) Jan 2021 -- June 2021}}\label{skyworks-solutions-software-engineer-intern-jan-2021-june-2021}}

Brought on to assist the audio deep learning team by performing machine
learning experiments, administering cloud resources (e.g., MongoDB and
TPU instances), and writing tests.

\begin{itemize}
\tightlist
\item
  Created a Python library for defining weighted finite-state
  transducers and applying operations (e.g., composition) based on
  technical papers.
\end{itemize}

\hypertarget{lucid-software-software-engineer-intern-june-2020-sep-2020}{%
\subsection{\texorpdfstring{Lucid Software \emph{· \small Software
Engineer (Intern)} \hfill \small June 2020 -- Sep
2020}{Lucid Software · Software Engineer (Intern) June 2020 -- Sep 2020}}\label{lucid-software-software-engineer-intern-june-2020-sep-2020}}

Developed new front-end components and refactored endpoints to support
front-end changes.

\begin{itemize}
\tightlist
\item
  \textbf{Stack}: Angular and Typescript frontend; Scala backend.
\end{itemize}

\hypertarget{cbt-nuggets-software-engineer-intern-june-2018-june-2019}{%
\subsection{\texorpdfstring{CBT Nuggets \emph{· \small Software Engineer
(Intern)} \hfill \small June 2018 -- June
2019}{CBT Nuggets · Software Engineer (Intern) June 2018 -- June 2019}}\label{cbt-nuggets-software-engineer-intern-june-2018-june-2019}}

Worked on the mobile apps team (part-time during college) developing for
iOS and tvOS.

\switchcolumn

\hypertarget{about}{%
\section{About}\label{about}}

Software engineer with 5 years of professional experience, expertise in
leveraging functional techniques and type systems to prevent bugs, and a
track record of success in environments ranging from early startups to
massive enterprises.

\raggedright

\hypertarget{education}{%
\section{Education}\label{education}}

\textbf{Oregon State University}

\hypertarget{b.s.-computer-science-4.0-gpa-20172021}{%
\subsubsection{B.S., Computer Science (4.0 GPA)
2017--2021}\label{b.s.-computer-science-4.0-gpa-20172021}}

Relevant courses: Programming Language Fundamentals (Haskell) \& Deep
Learning.

\hypertarget{projects}{%
\section{Projects}\label{projects}}

\textbf{\href{http://julianfortune.com/lovelace/}{Lovelace}} --- A shift
schedule designer developed with React and TailwindCSS.

\textbf{\href{https://github.com/Tereshchenkolab/paper-ecg}{PaperECG}}
--- An application that digitizes ECGs built with PyQt.

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\vspace{1pt}

\href{https://doi.org/10.1101/2021.07.13.21260461}{Digitizing ECG image:
A new method and open-source software code}\\
\emph{Computer Methods and Programs in Biomedicine, June 2022.}

\href{https://doi.org/10.1177/1071181320641076}{Real-Time Speech
Workload Estimation for Intelligent Human-Machine Systems}\\
\emph{Human Factors and Ergonomics Society Annual Meeting, 2020.}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\textbf{Languages:} Python, Kotlin, Typescript, Scala (Typelevel),
Swift, \& Haskell.

\textbf{Cloud:} Object storage, Postgres, MongoDB, Redis, instances, \&
message queues.

\textbf{Tools:} Docker, Terraform, Gradle, \& Make.

\end{paracol}

% \end{raggedright}

\end{document}
